In this project, we gave readers a thorough overview of Secondary Frequency Control and PI control: the algorithms (PART I) and the test case scenario (Nordic) (PART II), as well as how we contributed to the analytical tools to connect the theories and testings. \\

In Chapter~\ref{Chapter2}, we walked through the overview of Frequency Control, including Primary Frequency Control, Secondary Frequency Control and Tertiary Frequency Control. We knew the reasons we need Frequency Control and the mechanisms of the three Frequency Controls. Equally important is that we knew the response time and the feature of the three Frequency Controls. \\

In Chapter~\ref{Chapter3}, we covered the theory elements of Secondary Frequency Control and PI control. We introduced the physical theory behind Secondary Frequency Control and the logic of a central control algorithm. We explained we need to simplify the model to remove some conditions that do not affect the simulation results. We introduced the mathematical and physical theory of PID control. Through the frequency problems in the reality, we understood the reasons of using P-term and the I-term in SFC and the reasons of not using D-term because of amplifying the high component parts in the signal. Then, we introduced the core codes in PI control in Python and how we sent the information into the generators to fix the frequency problems. Besides, we introduced the deadband error and discussed the deadband control algorithm. In the last part of this chapter, we introduced our tuning methodology. First, we analysed the impacts of ki and then we introduced bisection method into tuning models. Then, we introduced analytical models written in Python and MATLAB and finally they can be used in filtering unacceptable results according to signal requirements, in generating 2D diagram, and in generating 3D triangle surface plot with multiple needs. \\

In PART II, the key questions we wanted to answer are: Is there any feature of a PI control under the condition of low time delay? What are the impacts of time delay to such a PI controller? Where is the best tuning result? What are the impacts of the rate of change? What are the impacts of time delay to the emergency control? Is there any impact on the stability of the system?\\

In Chapter~\ref{Chapter4}, we put forward how to assume the conditions, i.e. hypothesis, of the Nordic system and finally, we choose suitable value of kp, ki, delay, start time, end time etc. Then, we discussed the expected outcome based on physical theory of SFC before the simulation starts. Then, we introduced how to tune PI control and finally we showed you the simulation results. We thought a larger kp responses faster but at the same time it can potentially exceed the speed limit of power output. Finally, we introduce the ramp rate which is significant in real life. It is concluded that the ramp rate can remove some unacceptable results but we need to set the limit of ramp rate reasonably.\\

In Chapter~\ref{Chapter5}, like in Chapter~\ref{Chapter4}, we put forward how to assume the conditions of the Nordic system and finally, we choose the range of time delay and keep the condition in Chapter 4. Then, we discussed the expected outcome based on physical theory of SFC before the simulation starts. Then, we introduced how to tune time delay and finally we showed you the simulation results. We think there are some outliers that will interfere the analysis so we decided to filter them. We concluded that acceptable results are less and kp and ki are shrank to each other with a larger time delay. \\

In chapter~\ref{Chapter6}, we discussed the impact of time delay under the condition of  Emergency Control. We concluded that there is no difference for Emergency Control and a SFC interns on the impact of time delay: the controllers are affected by the time delay. Besides, we analysed the ramp rate of the emergency control and compare it with the SFC. We concluded that the emergency control requires a larger ramp rate than the SFC needs. This poses a challenge to the stability of the grid in an emergency.\\

I am really excited about the progress that has been made for the past one academic year. At the same time, we also deeply believe that there is still a long way to go towards smart grid algorithms, and we are still facing challenges and a lot of open questions that need to be addressed in the future. For instance, we need spend more time on developing reasonable limits of ramp rate. We need to analyse every possible emergency situation and find a way to predict it and prevent it. Another challenge is that we need to keep designing more advanced algorithms. Algorithms like Artificial Neural Network (ANN) \cite{pandey2013literature}, \cite{chaturvedi1999load}, Genetic Algorithms \cite{pandey2013literature}, \cite{dangprasert1996genetic}, \cite{rerkpreedapong2003robust} and Particle Swarm Optimisation (PSO) Algorithms \cite{pandey2013literature}, \cite{hosseini2008adaptive} has been discussed in the area for years, but so far we haven't found a universal perfect algorithm yet.\\